\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{adjustbox}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{etoolbox}

% Automatically scale all tables to page width
\AtBeginEnvironment{tabular}{\begin{adjustbox}{max width=\textwidth}}
\AtEndEnvironment{tabular}{\end{adjustbox}}

\onehalfspacing

\title{Replication of Szymanowska et al.~(2014)\\
Short- and Long-Horizon Commodity Futures Premia}
\author{Daniil Garbuzov and Coauthor}
\date{\today}

\begin{document}
\maketitle

\section{Overview of the Replication Project}

This document summarizes our replication of Szymanowska et al.~(2014), who
study short- and long-horizon premia in commodity futures.
All statistics, tables, and figures shown here are generated directly by our
Python code from WRDS data and saved as \LaTeX{} files or images that we
input into this report.

Our goals were to (i) reconstruct the main tables in the paper (Tables~1 and
2), (ii) extend the sample through 2026, and (iii) provide additional summary
statistics and data snapshots that clarify the structure of the underlying
futures panel.
We intentionally do not show code; this document is a high-level narrative of
what we did and what we learned.

\section{Data Sources and Construction}

\subsection*{Data sources}

We rely on Thomson Reuters Datastream data obtained via WRDS:
\begin{itemize}
  \item \textbf{TR\_DS\_FUT}: daily futures settlement prices and contract
        information (symbol, contract code, maturity date).
  \item \textbf{TR\_DS\_COMDS}: continuous/spot commodity indices used for
        context and sanity checks.
\end{itemize}

From TR\_DS\_FUT we pull all available futures contracts for the commodities
used in the original paper and map each contract to a sector.
The main sectors are Energy, Meats, Metals, Grains, Oilseeds, Softs, and
Industrial Materials, and we also construct an equally-weighted ``All''
portfolio across all commodities.

\subsection*{Bimonthly panel and portfolio construction}

We convert the daily futures data into a bimonthly panel.
This involves:
\begin{itemize}
  \item Defining a grid of six observation dates per year (every two months).
  \item On each date, identifying available contracts at different times to
        maturity and computing corresponding futures prices.
  \item Forming equal-weighted sector portfolios by averaging log returns
        across commodities within each sector.
\end{itemize}

The resulting bimonthly panel is stored as \texttt{commodity\_panel.parquet}
and serves as the input for constructing Short Roll (SR) and Excess Holding
(EH) returns, which are saved in \texttt{returns\_panel.parquet}.

\section{Understanding the Underlying Data}

To give the reader a concrete sense of the data we work with, we first show a
small excerpt of the commodity panel and then provide sector-level summary
statistics and lists of commodities and sectors.
All of these tables are generated by Python and exported as \LaTeX{}
snippets.

\subsection*{Head of the commodity panel}

The first table below displays the first few rows of the bimonthly commodity
panel.
This table is created by taking the head of
\texttt{commodity\_panel.parquet} and converting it to \LaTeX.

\begin{table}[h]
  \centering
  \caption{Head of the bimonthly commodity panel.
  The table shows a few rows of the panel used to construct SR and EH returns,
  including observation dates, commodity identifiers, sectors, and prices at
  several maturities.}
  \label{tab:panelhead}
  \resizebox{\textwidth}{!}{%
    \input{../_output/commodity_panel_head.tex}
  }
\end{table}

\subsection*{List of sectors and commodities}

The following tables report the distinct sectors present in the panel and
list the individual commodities and their sector assignments.
Both are generated directly from the underlying panel by grouping and
exporting to \LaTeX.

\begin{table}[h]
  \centering
  \caption{List of sectors in the commodity panel.
  This table summarizes the sector classification used throughout the
  replication (Energy, Meats, Metals, Grains, Oilseeds, Softs, Industrial
  Materials, and an equally-weighted ``All'' portfolio).}
  \label{tab:sectors}
  \input{../_output/sectors_list.tex}
\end{table}

\begin{table}[h]
  \centering
  \caption{List of commodities and their sectors.
  The table maps each individual commodity in the panel to a sector, which is
  the basis for the sector-level equal-weighted portfolios used in all
  subsequent analysis.}
  \label{tab:commodities}
  \input{../_output/commodities_list.tex}
\end{table}

\subsection*{Summary statistics for SR returns}

We next present sector-level summary statistics for the bimonthly Short Roll
return \(sr_1\) (one-period SR).
These statistics are computed from \texttt{returns\_panel.parquet} and
exported to \texttt{summary\_stats.tex}.

\begin{table}[h]
  \centering
  \caption{Summary statistics for bimonthly \(sr_1\) returns by sector.
  For each sector, we report the mean, standard deviation, range, skewness,
  and kurtosis of the \(sr_1\) series.}
  \label{tab:summary}
  \input{../_output/summary_stats.tex}
\end{table}

\section{Short Roll and Excess Holding: Formulas}

Let \(S_t\) denote the spot price at time \(t\) and \(F_t^{(n)}\) the
futures price at time \(t\) for a contract maturing \(n\) bimonthly periods
ahead.
We observe data at bimonthly dates \(t = 0,1,2,\dots\) (six per year).

\subsection*{Short Roll (SR) returns}

For a given horizon \(n\) (in bimonthly periods), the SR strategy rolls
futures contracts to maintain a constant time to maturity \(n\).
The bimonthly log SR return from \(t\) to \(t+1\) at horizon \(n\) is
\[
  r^{\text{SR},n}_{t \to t+1}
  = \ln F_{t+1}^{(n)} - \ln F_t^{(n)}.
\]
In the data, we denote these returns by \(sr_n\) for \(n = 1,2,3,4\).
For each sector, we average \(sr_n\) across commodities and then compute
annualized moments:
\[
  \mu_{\text{ann}}^{\text{SR},n}
  = \mu_{\text{raw}}^{\text{SR},n} \times 6, \quad
  \sigma_{\text{ann}}^{\text{SR},n}
  = \sigma_{\text{raw}}^{\text{SR},n} \times \sqrt{6},
\]
where \(\mu_{\text{raw}}^{\text{SR},n}\) and \(\sigma_{\text{raw}}^{\text{SR},n}\)
are the mean and standard deviation of the bimonthly SR returns \(sr_n\).

\subsection*{Excess Holding (EH) returns}

The EH strategy compares holding a contract to maturity to rolling at a
constant horizon.
For a maturity of \(n\) bimonthly periods, the log EH return over \(n\)
periods is
\[
  r^{\text{EH},n}_{t \to t+n}
  = r^{\text{Hold},n}_{t \to t+n}
    - r^{\text{SR},n}_{t \to t+n},
\]
where \(r^{\text{Hold},n}_{t \to t+n}\) is the return from buying an
\(n\)-maturity contract at \(t\) and holding it to \(t+n\), and
\(r^{\text{SR},n}_{t \to t+n}\) is the cumulative SR return over the same
horizon.
In the data, we denote these by \(eh_n\) for \(n = 2,3,4\).

Because EH returns span \(n\) bimonthly periods, we annualize their moments
using
\[
  \mu_{\text{ann}}^{\text{EH},n}
  = \mu_{\text{raw}}^{\text{EH},n} \times \frac{6}{n}, \quad
  \sigma_{\text{ann}}^{\text{EH},n}
  = \sigma_{\text{raw}}^{\text{EH},n} \times \sqrt{\frac{6}{n}}.
\]

\subsection*{Newey--West \(t\)-statistics}

To compute \(t\)-statistics for the mean returns, we run a simple regression
\[
  r_t = \alpha + \varepsilon_t,
\]
where \(r_t\) is the bimonthly SR or EH return.
We then estimate \(\hat{\alpha}\) and its Newey--West robust standard error
\(\text{SE}_{\text{NW}}(\hat{\alpha})\) using a lag length that accounts for
overlapping returns (at least \(n-1\) for EH) and a rule-of-thumb based on
the sample size.
The reported \(t\)-statistic is
\[
  t_{\text{NW}} = \frac{\hat{\alpha}}{\text{SE}_{\text{NW}}(\hat{\alpha})}.
\]

\section{Challenges, Successes, and Takeaways}

\subsection*{Successes}

We view the replication as partially successful:
\begin{itemize}
  \item We built a transparent, fully reproducible pipeline from WRDS data to
        bimonthly sector and portfolio returns, SR and EH decompositions, and
        \LaTeX{} tables.
  \item We reproduced the overall structure and many of the qualitative
        findings of Tables~1 and~2 and extended both tables to 2026.
  \item We added summary statistics and data snapshots (panel head, commodity
        and sector lists) that make the empirical setting more interpretable.
\end{itemize}

\subsection*{Challenges}

The main obstacles were:
\begin{itemize}
  \item \textbf{Ambiguous implementation details}: the paper does not fully
        specify every aspect of contract filtering, roll timing, or treatment
        of missing prices, forcing us to make reasonable but unverified
        choices.
  \item \textbf{Data version differences}: our TR\_DS\_FUT and TR\_DS\_COMDS
        extracts may differ from those originally used, due to vendor
        revisions or historical changes in WRDS.
  \item \textbf{Sensitivity of portfolio regressions}: the portfolio-sorted
        results in Table~2 proved especially sensitive to small changes in
        implementation, making an exact match very difficult.
\end{itemize}

\subsection*{What we learned}

Overall, the project highlights the importance of:
\begin{itemize}
  \item Building robust, well-documented data pipelines for empirical asset
        pricing work.
  \item Stress-testing published results with extended samples and additional
        diagnostic tables and figures.
  \item Recognizing that even carefully executed replications may not produce
        identical numbers when key data and implementation details are not
        fully disclosed.
\end{itemize}


\clearpage
\appendix
\section*{Appendix A: Main Tables}

\begin{adjustbox}{max width=\textwidth}
\input{../_output/table1.tex}
\end{adjustbox}

\clearpage

\begin{adjustbox}{max width=\textwidth}
\input{../_output/table1_extended.tex}
\end{adjustbox}

\clearpage

\begin{adjustbox}{max width=\textwidth}
\input{../_output/table2.tex}
\end{adjustbox}

\clearpage

\begin{adjustbox}{max width=\textwidth}
\input{../_output/table2_extended.tex}
\end{adjustbox}
\end{document}
